\documentclass{article}
\usepackage[utf8]{inputenc}

\title{PS1}
\author{Christin Bivens}
\date{January 2018}

\begin{document}

\maketitle

\text{My interests in programming and economics can be summed up by the fact that both can be used for any problem or area of study. My academic interests and strengths lean toward creative problem solving, critical thinking, and using observation to make a big picture out of lots of details. Previously, I studied fine arts (I like it all: painting, drawing, ceramics). The arts, data science, and economics all share a focus on relationships. How do these two colors play off each other and what does that communicate? How do these two variables interact and what does that mean? These questions require different tools but the same thought process. This focus on relationships lends itself toward experimentation and a hunt for understanding, which I will never find boring. I hope to take this degree and find a job in any industry that allows for me to keep asking questions and looking at connections to understand the situation at hand - and find answers! This class seems to promise the practical skill set to make this happen. I intend to study something within the fashion industry with my final project. The affinity for the fashion industry that I have is probably due to the fact that it's a merger of practical art and capitalism. It's not necessarily a goal of mine to work in the fashion industry, but it endlessly fascinates me. There seems to be a lack of business knowledge in the industry, brands tend to have a hard time being profitable or sustainable economically. There is a void to be filled, and new territory to be explored to help make these artists more efficient and therefore, more profitable.}

\section{a^2 + b^2 = c^2}


\end{document}
